|

### 2022-02-27 paper/dcpo_demsupport.Rmd
add osf source for dcpo_ajps, apsr, input, and exp_claassen_input @sammo3182

```{r data-input, include=FALSE}
## Replication data
load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
load(here("data", "correct_cls_apsr.rda")) # https://osf.io/cws59/download
load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/cgxjd/download
load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/uka5g/download
load(here("data", "exp_claassen_input.rda")) # Source???

@@

```{r dcpodata-input, include=FALSE}
## Replication data
load(here("data", "dcpo_ajps.rda"))  # https://osf.io/xxxx/download
load(here("data", "dcpo_apsr.rda"))  # https://osf.io/xxxx/download
load(here("data", "dcpo_input_update22.rda"))  # https://osf.io/xxxx/download

>>>>

```{r data-input, include=FALSE}
## Replication data
load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
load(here("data", "correct_cls_apsr.rda")) # https://osf.io/cws59/download
load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/cgxjd/download
load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/uka5g/download
load(here("data", "exp_claassen_input.rda")) # https://osf.io/fcyn3/download

@@

```{r dcpodata-input, include=FALSE}
## Replication data
load(here("data", "dcpo_ajps.rda"))  # https://osf.io/xw9fr/download
load(here("data", "dcpo_apsr.rda"))  # https://osf.io/j7kn3/download
load(here("data", "exp_dcpo_input.rda"))  # https://osf.io/r2pe8/download
